%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CV In LaTeX
%
% Edited by:
% John Keaney
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{John Keaney} % Your name
\address{29 Fitzroy Avenue, Drumcondra, Dublin, Ireland} 
\address{087 687 0657 \\ keaneyjo@tcd.com} 

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education \& University}

{\bf Second Year Student at Trinity College Dublin, Ireland} \hfill {\em August 2018 - Present}
\\ Integrated Computer Science
\\ Bachelor's Degree In Process\\
\\{\bf Entertainment Officer at Dublin University Computer Science Society} {\em August 2019 - Present} 
\\Organised Events for Speakers including Google, Microsoft, Hubspot \& Arista.
\\Head Organiser behind Trinity Computer Science Ball.
\\Co-host of Hackathons, including Arista Hackaton \& TCD First Year Hackaton.
\\
%Currently working on organising DU Hackatons aswell as Computer Science Ball
\\{\bf St. Clares Comprehensive School, Leitrim} \hfill {\em August 2012 - June 2018} 
\\ Elected as Senior Prefect of Student Council in my Final Year.
%\\ Second Highest Leaving Certificate Results of Year Among Male Students.
%\href{http://www.youtube.com}{Youtube}
% 1st year Coding Competition
% Arista Coding Competition
% Young Scientist

%-------------------------------------------------------------------------------
%    Projects
%-------------------------------------------------------------------------------

\begin{rSection}{\href{https://github.com/Keaneyjo}{Pinned Projects}} %Add links to github for each one
\href{https://github.com/Keaneyjo/C-Huffman-Tree-Encoder}{{\bf Huffman Binary Tree Encoder}}\\
A C program which creates a Huffman Binary Search Tree from a sample .txt file. Then encodes said file via the Huffman Tree into a series of binary digits. The purpose of this is to provide efficient memory storage through encrypting and decoding.

\href{https://github.com/Keaneyjo/Hacker-News-Interface}{{\bf Hacker News Processing Interface}}\\ 
A Front End Interface developed using Processing. The program preforms on analysis of 4GB of User Stories and Profiles to create a display similar to that of .

\href{https://github.com/Keaneyjo/Command-Control-Networking-Protocol}{{\bf Command \& Control Networking Protocol}}\\
Programmed in Java, this protocol uses a synchronized series of methods to send a Datagram Packet to a series of Nodes; from Client to Broker and then forwards to Workers. The Program makes use of a Datagram Packet Structure and manipulation to effectively communicate between Nodes.

\href{https://github.com/Keaneyjo/Connect-4-Arm-Assembly}{{\bf Connect 4 Arm Assembly}}\\
A Connect Four Game written in Arm Assembly code for My Computing II Module. The code implements an "A.I. User" or two-player multi-player. Inputs and outputs are printed through the UART window using ASCII-Art. The board makes use of Matrices to compute the winning result.

\end{rSection}
\end{rSection}

\begin{rSection}{Academic Achievements /Programming Experience}
{\bf Achievements:}\\
- Third Place Winner of BT Young Scientist Behavioural Sciences Senior Individual Category.\\
- Recipient of Josie Martin Scholarship (2019).\\
{\bf Programming Specific:}\\
- Invited to Google Open House Ireland (2019/20).\\
- Arista Coding Tournament Competitor.\\
- TCD 1st Year Java Programming Competitor.\\
- Bloomberg Capture The Flag Competitive Participant.

%
%DUCSS Inaugural - Google's Stian Lauvstad. - Microsoft's Stephen Howell.
%Arista Open Evening
%

\end{rSection}



\begin{rSection}{Contact / Additional Links} 
% Email
% Email:  \hfill {\em keaneyjo@tcd.ie}\\
% Phone Number
%Phone Number:   \hfill {\em 087 687 0657}\\
% Github
\href{https://github.com/Keaneyjo}{Github Repositories} 
\hfill {\href{https://github.com/Keaneyjo}{\em github.com/Keaneyjo}}\\
% LinkedIn
\href{https://www.linkedin.com/in/john-k-9a5247104/}{LinkedIn Profile}  
\hfill {\href{https://www.linkedin.com/in/john-k-9a5247104/}{\em linkedin.com/in/john-k-9a5247104/}} \\
\end{rSection}



\end{document}




% Initial Projects Template

%{\bf Dynamic Analysis of Buckling Restrained Braces} 
%\\The project aims at designing and fabrication of two Buckling Restrained Braces which were analyzed under dynamic loading. As alternative for conventional braces, these BRBs are also beneficial for seismic retro-fitting in RCC and steel structures.\\
%\\{\bf Indirect Model Analysis of Structures}\\
%Presented a Seminar on Indirect Model Analysis, explaining the method to compute response of Prototype from the Influence lines obtained from Model. Use of Muller Breslau Principle in Indirect Model Analysis and the Similitude between prototype and  model.\\
%\\{\bf Microtunneling}\\
%Presented a seminar on Micro Tunneling, explaining its advantages over conventional method of drainage laying systems. Analysis considering direct and indirect cost of micro tunneling was also discussed.
