
\documentclass[]{rahulworld-resume}

\usepackage{hyperref}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 
\begin{large}
	\headername{John Keaney}\\
\end{large}
Third Year Student\\
Integrated Computer Science (B.Arts)\\ 
@ Trinity College Dublin\\ 
Second Year Grading: Overall 79\% (First)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Links} 
\noindent\rule{5cm}{0.4pt}


LinkedIn://  \href{https://www.linkedin.com/in/john-keaney/}{\custombold{john-keaney}} \\
Github:// \href{https://github.com/Keaneyjo}{\custombold{Keaneyjo}}
%Behance://  \href{https://www.behance.net/rahul_world}{\custombold{rahul\_world}}

% Maybe put a medium profile here
% Or a gitgud
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\noindent\rule{5cm}{0.4pt}
\vspace{6pt}
\subsection{Languages}
Java, C, Assembly, Processing\\
HTML, CSS, JavaScript\\
Prolog, Python\\

% Flappy Bird
% https://youtu.be/AWcNFv0VnSA

%JavaScript, Phyton, HTML/CSS, C++
\vspace{6pt}
\subsection{Framework}
OpenCV.js, Node.js\\
React Native, Expo, Cordova\\


\vspace{6pt}
\subsection{Others}
Linux, Windows, Git, Vim,\\
IntelliJ, VS Code, Eclipse\\
Neural Networks, Genetic Algorithms\\
Adobe Photoshop, After Effects

\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coursework}
\noindent\rule{5cm}{0.4pt}

Object-Oriented Programming\\
Software Engineering Project\\
Data Structures \& Algorithms\\
Discrete Mathematics\\
Systems Programming\\
Computer Architecture\\

\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 
\noindent\rule{5cm}{0.4pt}\\
\datecolor{2018-2022}
\subsection{Third Level Education}
B.Arts. in Integrated Computer Science
Trinity College Dublin \\
Grade : First (Predicted)\\

%\vspace{8pt}
%\datecolor{20XX-20YY}
%\subsection{Intermediate}
%Hame Convent Inter College, FZD\\
%Percentage: 80.8\%\\

\vspace{8pt}
\datecolor{2013-2018}
\subsection{Second Level Education}
Leaving Certificate \\
St.Clares Comprehensive\\
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 
% \descript{BS in Computer ence}
\hspace*{0pt}\hfill 17 Grand Canal,    \\
\hspace*{0pt}\hfill James Street,    \\
\hspace*{0pt}\hfill Dublin 8, D08 T3K8\\
\hspace*{0pt}\hfill  \\
\hspace*{0pt}\hfill Mob.: +353-87687 0657 \\
\hspace*{0pt}\hfill Email.:\textbf{\href{mailto:keaneyjo@tcd.ie}{keaneyjo@tcd.ie}} \\
%\hspace*{0pt}\hfill Web.:\textbf{\href{http://rahulchauhan.net}{http://rahulchauhan.net}} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Work Experience}
\noindent\rule{12.5cm}{0.4pt}
\datecolor{2019-2020} \runsubsection{SureWash Software Engineer}
\descript{SureWash}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
I worked with the Hygiene Company SureWash, under guidance of the CTO in App Design. Acted as the lead in UI Design and primary liaison between the CTO and my team. Worked on Front-End Development through React-Native but later switched to Cordova + JavaScript.
\end{minipage}
\descriptright{HTML, CSS, JavaScript, OpenCV.js, Cordova, React Native, Expo, Node.js}
\sectionsep

\datecolor{2020-Now} \runsubsection{COVID-19 Officer}
\descript{St.Clares Comprehensive}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Prepared Learning Environment for Secondary School Students. Introduced Sanitation Protocols around the building.
\end{minipage}

\datecolor{2019-2019} \runsubsection{Leaving Certificate Scribe}
\descript{St.Clares Comprehensive}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Reading \& Writing Aid for 6th Year Students of the 2019 National Leaving Certificate Exams.
\end{minipage}

%\datecolor{2015-2019} \runsubsection{St.Clares Comprehensive School}
%\descript{Janitor}
%\noindent
%\hspace{5em}%
%\begin{minipage}{0.85\textwidth\vspace{2pt}}
%pan sharpening is one kind of data fusion become very wide spread method which p
%\end{minipage}
%\descriptright{}
%\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Achievements/ Extra-Curricular} 
\noindent\rule{12.5cm}{0.4pt}

\datecolor{2020-Now} \runsubsection{Dublin University Computer Science Society Secretary}
\descript{}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
As Secretary of Trinity's Computer Science Society (DUCSS), I act as the primary liaison between DUCSS and our Speakers, Organising €1000+ Sponsorship Contracts with Companies including Microsoft, Amazon and SIG. 
%My duties includes sending Weekly emails, forming executive decisions and attending meetings with our collaborators.
\end{minipage}

\datecolor{2018-2019} \runsubsection{DU Computer Science Society Entertainments Officer}
\descript{}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Provided hosting for Events for Google, Microsoft, Hubspot \& Arista. Head Organiser of CS Ball with 140+ Attendees. Co-host for Hackatons including Arista Hackaton \& TCD 1st Year Hackaton.
\end{minipage}

\datecolor{2020-SUM} 
\runsubsection{Trinity Book Prize Winner}
\descript{}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Students who receive 90\% or higher in one or more module are recipient of Trinity's Book Prize Award.
\end{minipage}

\datecolor{2017-WINT} \runsubsection{BT Young Scientist Winner}
\descript{}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
3rd Place Winner of Senior Individual Behavioural Science Category @ BT Young Scientist. 
%My paper was a "Comprehensive Anaylsis of Student's Attendance and Grading" which was processed using Microsoft Excel.
\end{minipage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SIDE PROJECT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Side Projects}
\noindent\rule{12.5cm}{0.4pt}
%\datecolor{2019-2020} 
\runsubsection{\href{https://github.com/Keaneyjo/SureCoverage}{SureCoverage COVID-19 App}} \href{https://www.youtube.com/watch?v=t-JP8o0rwPQ}{\{Video Link\}}
\descript{OpenCV.js, Image Processing}
\noindent
%\hspace{5em}%
\begin{minipage}{1\textwidth\vspace{5pt}}
A Germ Detection Scanner App coded in Cordova during my time at SureWash. The app used the OpenCV.js library to detect Hand Movement and return a Hand Sanitation Heat Map. Contain's an interactive tutorial and COVID resources.


 
\end{minipage}


%\datecolor{2020-SUM} 
\runsubsection{\href{https://github.com/Keaneyjo/neuro_evolved_flappybird}{NeuroEvolved Flappy Bird}}
\href{https://www.youtube.com/watch?v=AWcNFv0VnSA&feature=youtu.be}{\{Video Link\}}
\descript{Neural Networks, Processing}
\noindent
%\hspace{5em}%
\begin{minipage}{1\textwidth\vspace{5pt}}
Using the Toy Neural Network Library and a generic Genetic Algorithm this Processing program trains a wave of birds to win the game of "Flappy Bird".
\end{minipage}




%\datecolor{2019-SPRI} 
\runsubsection{\href{https://github.com/Keaneyjo/Connect-4-Arm-Assembly}{Connect 4: AI Opponent}}
\descript{Keil uVision, Assembly}
\noindent
%\hspace{5em}%
\begin{minipage}{1\textwidth\vspace{5pt}}
A Connect 4 program which implements an "A.I. User" or two-player multi-player. The A.I predicts what moves it needs to win to make based on the players history.
\end{minipage}







%\datecolor{2019-WINT} 
\runsubsection{\href{https://github.com/Keaneyjo/C-Huffman-Tree-Encoder}{Huffman Binary Tree Encoder}}
\descript{Huffman Trees, Encoding \& Encryption}
\noindent
%\hspace{5em}%
\begin{minipage}{1\textwidth\vspace{0pt}}
A C program which creates a huffman binary tree from a sample .txt file. Then encodes said file via the huffman tree into a series of binary digits. The program can then decode the file using that same huffman tree.
\end{minipage}


\end{minipage} 
\end{document}  \documentclass[]{article}

