\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.75in,top=0.3in,right=0.75in,bottom=0in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.1\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{John Keaney} % Your name
\address{Toothfield, Manorhamilton, Co.Leitrim}
\address{087 687 0657 \\ keaneyjo@tcd.ie} % Your phone number and email

\begin{document}

%--------------------------------------------------------------------------------
%    Education
%---------------------------------------------------------------------------------
\begin{rSection}{Education}
{\bf Integrated Computer Science Student, Trinity College Dublin} \hfill {\em August 2018 - Present}
\\ Second Year Student, School Of Computer Science and Statistics

%\\{\bf St.Clares Comprehensive School} \hfill {\em September 2012 - June 2018} 
%\\ Elected as Senior Prefect of Student Council in my Final Year.
\end{rSection}


%--------------------------------------------------------------------------------
%    Previous Work Experience
%---------------------------------------------------------------------------------
\begin{rSection}{Previous Work Experience}
{\bf Software Engineer Student for SureWash}\hfill {\em January 2020 - April 2020}\\
I worked with the hygiene company SureWash, under the guidance of the CTO in App Design. Majority of my work involved the creation of a Germ Detection App using JavaScript and the OpenCV.js Library.

{\bf Leaving Certificate Scribe}\hfill {\em Summer of 2019}\\
Reading \& Writing Aid for Leaving Certificate Students

\end{rSection}


%-------------------------------------------------------------------------------
%    Projects
%-------------------------------------------------------------------------------

\begin{rSection}{\href{https://github.com/Keaneyjo/}{Projects}} %Add links to github for each one
\href{https://github.com/Keaneyjo/SureCoverage}{{\bf SureWash SureCoverage Germ Detection App}}\\
A Germ Detection Cross-platform App written in JavaScript. Built using the Cordova Framework and OpenCV.js Library. Functionality also includes Hand Sanitation Tutorials \& Info on COVID-19.


\href{https://github.com/Keaneyjo/C-Huffman-Tree-Encoder}{{\bf Huffman Binary Tree Encoder}}\\
C program which creates a Huffman Binary Search Tree from a sample .txt file. Used to provide efficient memory storage through encrypting and decoding.

\href{https://github.com/Keaneyjo/Hacker-News-Interface}{{\bf Hacker News Interface Clone}}\\
A Front End Interface developed using Processing. The program preforms on analysis of 4GB of User Stories and Profiles to create a user-friendly UI fitted with statistics on the content of the data provided.

\href{https://github.com/Keaneyjo/Command-Control-Networking-Protocol}{{\bf Command \& Control Networking Protocol}}\\
Programmed in Java, this protocol uses a synchronized series of methods to send a Datagram Packet from Client to Broker and then forwards to Workers.

\href{https://github.com/Keaneyjo/Connect-4-Arm-Assembly}{{\bf Connect 4 A.I. Assembly}}\\
A Connect 4 Game written in Assembly code. The code implements an "A.I. User" or 2-player multi-user. Results printed via UART with ASCII-Art. Matrix Multiplication used to compute winner.

%A Connect Four Game written in Assembly code. The code implements an "A.I. User" or two-player multi-player. Inputs and outputs are printed through the UART window using ASCII-Art. The board makes use of Matrices to compute the winning result.

\end{rSection}







%----------------------------------------------------------------------------------
%	Society / Volunteer Work
%----------------------------------------------------------------------------------
\begin{rSection}{Society / Volunteer Work}
{\bf TCD Computer Science Society Secretary} \hfill {\em February 2020 - Present}
\\Primary liaison between DUCSS and our Speakers, Organising 1000 Euro+ Sponsorship Deals with Companies including Microsoft, Amazon and SIG. 

{\bf TCD Computer Science Society Entertainments Officer} \hfill {\em September 2019 - April 2020}
\\ Hosting for Events including Google, Microsoft, Hubspot \& Arista. Head Organiser of CompSci Ball with 140+ Attendees. Co-host of Hackathons, including Arista Hackaton \& TCD First Year Hackaton.

{\bf Undergraduate Programming Centre} \hfill {\em September 2018 - Present}
\\ Mentorship Program to help new students with their academics when appropriate.

\end{rSection}









%----------------------------------------------------------------------------------
% Other
%----------------------------------------------------------------------------------
\begin{rSection}{Other} 
{\bf Programming Languages} \hfill
 Java, C, Assembly, JavaScript, React-Native, MATLAB, Git, Cordova
 {\bf Programming Activities:}\\
- TCD 1st Year Java Competition Top 10.\\
- Arista Coding Tournament Competitor Top 20.\\
- Invited to Google Open House Ireland (2019/20).\\
- Google HashCode Competitor (2020).\\


%Advanced French Module \hfill {\em First Achieved}\\
%Young Scientist Winner \hfill 3rd Place in Behavioural Science\\


\end{rSection}




\end{document}




%------------------
%     Notes
%-------------------
% Add SureWash Project
% Microprocessors Projects?
% Concurrency Projects?
